---
title: "Homework 1"
author: Beibei Cao
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements. 

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the means of numbers and logical but not character or factor.


Use `as.numeric` function to convert variables from one type to another.

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

Convert the logical vector to numeric, and multiply the random sample by the result.
```{r logic_to_num}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```

Convert the logical vector to a factor, and multiply the random sample by the result.
```{r logic_to_factor}
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
```

Convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
```{r ogic_to_factor_to_num}
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

why not `$`
```{r}
prob1_df$samp

pull(prob1_df, samp)

prob1_df[["samp"]]
```


## Problem 2

Use the code below to download the package containing the `penguins` dataset:

```{r eval = FALSE}
install.packages("palmerpenguins")
```

Load the data and take a look:
```{r load_and_view}
data("penguins", package = "palmerpenguins")
head(penguins)
```

Description: 
the `penguins` dataset includes the following variables: ``r names(penguins)``; it has ``r nrow(penguins)`` rows and ``r ncol(penguins)`` columns. The mean of the flipper length is ``r mean(na.omit(pull(penguins, flipper_length_mm)))`` mm.

Make a scatterplot of `flipper_length_mm `(y) vs `bill_length_mm` (x); color points using the `species` variable.

```{r plot_and_save}
ggplot(na.omit(penguins), aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + xlab("bill length (mm)") + ylab("flipper length (mm)")

ggsave("scatter_plot.pdf", height = 4, width = 4)
```





